\documentclass[10pt]{resume}
\name{Pavel Panchekha}
\begin{document}
\maketitle
\contact{Address}{739 Mill Grove Drive, Audubon, PA 19403; (215)\thinspace555-2216}

\section{Job Objective} 

A summer position that will use my accounting and computer
skills.          
 
\section{Education}  
        
Rensselaer Polytechnic Institute, Troy, NY  \\        
Bachelor of Science, Management, May 1990   \\       
Concentration in Management Systems       \\   
Minors in Computer Science and Economics  \\        
G.P.A. 3.3/4.0    

\section{Experience}
\withright{Telefund Associate}{Rensselaer Fund}{Fall 1987-Present\\\>Troy, NY}
Generated alumni and parent support to reduce tuition,          
increase scholarship and financial aid funds; averaging 80          
percent pledge rate. Top three percent associate.

\withright{Team Programmer}{Group W Cable, Westinghouse Corp}{Summer 1987\\\>Mahway, NJ}
Liaison between accounting department and controller,          
provided assistance with invoice liabilities after          
divestiture of Group W Cable by Westinghouse.

\withright{Sales Assistant}{AP Technical Sales Inc.}{Summers  1985-86\\\>Palisades Park, NJ}
Duties included telemarketing, data entry, and invoicing.          
Successfully converted catalog inquiries to sales          
opportunities by telemarketing program.          


\section{Computer Skills}  
\begin{bullets}
\item Extensive knowledge of hardware and software for IBM PC and MTS. \\
\item Proficient programming skills in COBOL, WATFIV (FORTRAN), and BASIC.
\end{bullets}
 
\section{Honors and Awards}          
Epsilon Delta Sigma: Honorary Management Society at          
Rensselaer    \\      
Dean's List of Distinguished Students: Fall 1986-Spring 1988  \\        
National Honor Society: Northern Highlands High School  \\        
Creative Essay Award: Northern Highlands High School  \\        
Meritorious Action Life Saving Award: Boy Scouts of America          
 
\section{Extracurricular Activities}          
Epsilon Delta Sigma Public Relations Committee \\         
Rensselaer Ski Club     \\     
Bergen County Task Force Student Liaison 1986  \\        
LEADD (Legislators and Educators Against Drunk Driving) Chairman
1985-86  \\        
Youth Group - Temple Beth Or Activities Chairman 1985-86          

\end{document}
